Temporality of the Victorian Hospital Patient Transfer Network

### 2025-05-20 reports/_model.qmd
small content adds
Add some work

:::{#fig-general-diagram}
```{.tikz}
%%| format: svg
%%| filename: movement_general_case
%%| img-width: 800
%%| fig-cap: general movement processes
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, shapes.arrows}

\begin{tikzpicture}[
  node distance=2cm and 4cm,
  >=latex
]
  \tikzset{
    squarx/.style= {
      regular polygon,
      regular polygon sides=4
    }
  }
  \tikzset{
    house/.style= {
      single arrow,
      shape border rotate=90,
      single arrow head extend=0pt,
      single arrow tip angle=120,
      minimum height=0.75cm,
      minimum width=0.75cm
    }
  }

  \node[draw, squarx] (A) {$u$};
  \node (X) [right=of A] {};
  \node[draw, squarx] (B) [right=of X] {$v$};
  \node[draw, house] (H) [below=of X] {$h_{uv}$};
  \node[draw, circle] (D) [above=of X] {$\emptyset$};

  \draw[->] (A) edge node[above]{$d_{uv}(s, t)$}  (B);
  \draw[->] (A) edge node[above left]{$\zeta_u(s)$} (D);
  \draw[->] (A) edge node[below left]{$\eta_{uv}(s,t)$} (H);
  \draw[->] (H) edge node[below right]{$\rho_{uv}(s,t)$} (B);
\end{tikzpicture}
```

@@

$$\begin{aligned}
\lambda(u(s) \to \emptyset) &= \zeta_u(s)\\
\lambda(u(s) \to v(t)) &= d_{uv}(s, t)\\
\lambda(u(s) \to z_{uv}(t)) &= \eta{uv}(s, t)\\
\lambda(z_{uv}(t) \to v(t)) &= \rho_{uv}(s, t)
\end{aligned}$$

@@

$$\begin{aligned}
\lambda(u(s) \to {z'}_{uv}(t)) &= \eta_{uv}(s, t)\\
\lambda({z'}_{uv}(t) \to z_{uv}(t)) &= \delta(t \mathrm{ mod } \omega)\\
\end{aligned}$$

@@

For the temporal network, we make a choice of the time discretisation $\omega$. That is, events that occur within a time window $[\tau, \tau+\omega)$ are collapsed and aggregated to occur at time $\tau$. Over the observation (and simulation) period, we will have a series of time window boundaries $\{\tau_0, \tau_1, \dots\}$. We denote the smallest value in that set larger than a given time $t$ to be $\ceil{t}_\omega$
For the readmission process, we assume that individuals that would readmit within a given time window $[\tau, \tau+\omega)$ do so uniformly. 
This yields:

$$d_{uv}(s, t) = \frac{\sum_{t: (t-s) < \omega} w_{uv}(s, t)}{\omega N_u}$$
$$\eta_{uv}(s, t) = \frac{\sum_{t: (t-s) \geq \omega} w_{uv}(s, t)}{\omega N_u}$$
$$\rho_{uv}(s,t) = \frac{1}{\ceil{t}_\omega - t}$$

>>>>

:::{#fig-general-diagram}

![](diagrams/movement_general_case.pdf)

@@

$$\begin{aligned}
\lambda(u(s) \to \emptyset) &= \zeta_u(s)\\
\lambda(u(s) \to v(t)) &= d_{uv}(s, t)\\
\lambda(u(s) \to z_{uv}(s, t)) &= \eta_{uv}(s, t)\\
\lambda(z_{uv}(s, t) \to v(t)) &= \rho_{uv}(s, t)
\end{aligned}$$

@@

$$\begin{aligned}
\lambda(u(s) \to {z'}_{uv}(s)) &= \sum_t \eta_{uv}(s, t)\\
\lambda({z'}_{uv}(t) \to z_{uv}(t)) &= \delta(t \mod\omega)\\
\end{aligned}$$

@@

For the temporal network, we make a choice of the time discretisation $\omega$. That is, events that occur within a time window $[\tau, \tau+\omega)$ are collapsed and aggregated to occur at time $\tau$. Over the observation (and simulation) period, we will have a series of time window boundaries $\{\tau_0, \tau_1, \dots\}$. We denote the smallest value in that set larger than a given time $t$ to be $\lceil{}t\rceil{}_\omega$
For the readmission process, we assume that individuals that would readmit within a given time window $[\tau, \tau+\omega)$ do so uniformly. 
This yields:

$$d_{uv}(s, t) = \frac{\sum_{t: (t-s) < \omega} w_{uv}(s, t)}{\omega N_u}$$
$$\eta_{uv}(s, t) = \frac{\sum_{t: (t-s) \geq \omega} w_{uv}(s, t)}{\omega N_u}$$
$$\rho_{uv}(s,t) = \frac{1}{\lceil{}t\rceil{}_\omega - t}$$
